\tweetRowFull{Non-tagged}
{0.920}
{\joinNameTweet
{User\_70}
{RT @User\_78: FLASH: \#Egypt's Mursi has left presidential palace, two presidency sources say after protesters, police clash outside.}}
{\joinNameTweet
{User\_63}
{RT @User\_78: FLASH: \#Egypt's Mursi has left presidential palace, two presidency sources say after protesters, police clash outside.}}
\tweetRowFull{Non-tagged}
{0.884}
{\joinNameTweet
{User\_70}
{It's time. RT @User\_84: hey guys - this is barack.  ready to answer your questions on fiscal cliff \& \#my2k.  Let's get started. -bo}}
{\joinNameTweet
{User\_68}
{RT @User\_84: hey guys - this is barack.  ready to answer your questions on fiscal cliff \& \#my2k.  Let's get started. -bo}}
\tweetRowFull{Non-tagged}
{0.782}
{\joinNameTweet
{User\_73}
{A white woman... RT @User\_81: A woman? RT @User\_71: ‘Fresh Prince' Star Alfonso Ribeiro Weds http://t.co/IfT3Zqlr}}
{\joinNameTweet
{User\_81}
{A woman? RT @User\_71: ‘Fresh Prince' Star Alfonso Ribeiro Weds http://t.co/iTrfZfeM}}
\tweetRowFull{Non-tagged}
{0.697}
{\joinNameTweet
{User\_85}
{RT @User\_83: hear @User\_76 on the radio one minute ago!! it was funny :D x}}
{\joinNameTweet
{User\_83}
{hear @User\_76 on the radio one minute ago!! it was funny :D x}}
\tweetRowFull{Non-tagged}
{0.579}
{\joinNameTweet
{User\_66}
{RIP Mr Brubeck. Take five. "@User\_62: Dave Brubeck, jazz icon, dead at 91. http://t.co/ae9UIRmP"}}
{\joinNameTweet
{User\_80}
{RT @User\_62: Dave Brubeck, jazz icon, dead at 91. http://t.co/sOrBOFBR}}
\tweetRowFull{Non-tagged}
{0.443}
{\joinNameTweet
{User\_86}
{@User\_64 OKC traded James Harden}}
{\joinNameTweet
{User\_60}
{Why WOULD OKC TRADE JAMES HARDEN????}}
\tweetRowFull{Non-tagged}
{0.359}
{\joinNameTweet
{User\_79}
{(that should have had a link to the Tina and Amy host Golden Globes article. But I'm too lazy to fix it now)}}
{\joinNameTweet
{User\_72}
{Genius Move: Tina Fey and Amy Poehler to Host 2012 Golden Globe Awards! http://t.co/zdc2hS8F}}
\tweetRowFull{Non-tagged}
{0.275}
{\joinNameTweet
{User\_77}
{@User\_74 are you excited to come to Australia and meet all your amazing fans like me? ;) xx \#asknialler 11}}
{\joinNameTweet
{User\_61}
{@User\_75 EXCITED TO COME BACK TO AUSTRALIA, cause we miss you lots xox \#asknialler}}
\tweetRowFull{Non-tagged}
{0.242}
{\joinNameTweet
{User\_79}
{All of @User\_69's \#captainhottie pirate puns for \#ouat are perfect. It's the reason we are twitter friends.}}
{\joinNameTweet
{User\_69}
{I apologize in advance for inappropriate pirate puns. \#sorryImnotsorry \#OUAT}}
\tweetRowFull{Non-tagged}
{0.139}
{\joinNameTweet
{User\_67}
{Forever my lady lol}}
{\joinNameTweet
{User\_65}
{@User\_82 just go get it!! Lol (the devil) aint I? Lol but I would lol}}
