\tweetRowFull{Retweet}
{1.0}
{\joinNameTweet
{User\_8}
{RT @User\_21: A H R B Q D W E F L M N S X G I J K O P C T V Y U Z -- Gotta love what the alphabet looks like in alphabetical order.}}
{\joinNameTweet
{User\_21}
{A H R B Q D W E F L M N S X G I J K O P C T V Y U Z -- Gotta love what the alphabet looks like in alphabetical order.}}

\tweetRowFull{Retweet}
{0.834}
{\joinNameTweet
{User\_18}
{RT @User\_1: A girlfriend would be great, but I'm already in a pretty committed relationship with alcoholism and bad decisions.}}
{\joinNameTweet
{User\_1}
{A girlfriend would be great, but I'm already in a pretty committed relationship with alcoholism and bad decisions.}}

\tweetRowFull{Retweet}
{0.768}
{\joinNameTweet
{User\_19}
{RT @User\_20: All the weird horny stuff between Glenn and Maggie on Walking Dead makes me very uncomfortable.}}
{\joinNameTweet
{User\_20}
{All the weird horny stuff between Glenn and Maggie on Walking Dead makes me very uncomfortable.}}

\tweetRowFull{Retweet}
{0.602}
{\joinNameTweet
{User\_2}
{RT @User\_4: Brandywine Came Out With Win, \#TeamBwine}}
{\joinNameTweet
{User\_4}
{Brandywine Came Out With Win, \#TeamBwine}}

\tweetRowFull{Retweet}
{0.522}
{\joinNameTweet
{User\_6}
{RT @User\_22: I just love Toy Story, all of them}}
{\joinNameTweet
{User\_22}
{I just love Toy Story, all of them}}

\tweetRowFull{Retweet}
{0.408}
{\joinNameTweet
{User\_3}
{RT @User\_13: Welp now you know}}
{\joinNameTweet
{User\_13}
{Welp now you know}}

\tweetRowFull{Retweet}
{0.303}
{\joinNameTweet
{User\_25}
{RT @User\_16: Facebook is down? Oh no, how are cancer and child abuse going to stop without all those likes? :(}}
{\joinNameTweet
{User\_11}
{RT @User\_9: Stop acting like we have ‘rights' on Facebook http://t.co/geE9NjHH}}

\tweetRowFull{Retweet}
{0.248}
{\joinNameTweet
{User\_6}
{RT @User\_15: going to be slightly awkward when Jahmene scans the xfactor winner's single in Asda}}
{\joinNameTweet
{User\_7}
{RT @User\_17: Jahmene is gonna be scanning James Arthers CD at ASDA now.. awks}}

\tweetRowFull{Retweet}
{0.132}
{\joinNameTweet
{User\_14}
{RT @User\_23: RG3 should give Michael Vick a class in scrambling.}}
{\joinNameTweet
{User\_12}
{RG3 running at 4G!}}

\tweetRowFull{Retweet}
{0.070}
{\joinNameTweet
{User\_10}
{RT @User\_24: It's Monday, User\_24! http://t.co/asOF9yPA}}
{\joinNameTweet
{User\_5}
{Mondays are like Zubats. Nobody likes Zubats.}}
