\tweetRowFull{Non-tagged}
{0.920}
{\joinNameTweet
{hypervocal}
{RT @Reuters: FLASH: \#Egypt's Mursi has left presidential palace, two presidency sources say after protesters, police clash outside.}}
{\joinNameTweet
{AntDeRosa}
{RT @Reuters: FLASH: \#Egypt's Mursi has left presidential palace, two presidency sources say after protesters, police clash outside.}}
\tweetRowFull{Non-tagged}
{0.884}
{\joinNameTweet
{hypervocal}
{It's time. RT @whitehouse: hey guys - this is barack.  ready to answer your questions on fiscal cliff \& \#my2k.  Let's get started. -bo}}
{\joinNameTweet
{ethanklapper}
{RT @whitehouse: hey guys - this is barack.  ready to answer your questions on fiscal cliff \& \#my2k.  Let's get started. -bo}}
\tweetRowFull{Non-tagged}
{0.782}
{\joinNameTweet
{Mrjscott}
{A white woman... RT @T\_dot\_Lee: A woman? RT @majic1021: ‘Fresh Prince' Star Alfonso Ribeiro Weds http://t.co/IfT3Zqlr}}
{\joinNameTweet
{T\_dot\_Lee}
{A woman? RT @majic1021: ‘Fresh Prince' Star Alfonso Ribeiro Weds http://t.co/iTrfZfeM}}
\tweetRowFull{Non-tagged}
{0.697}
{\joinNameTweet
{wulan\_kyuufilan}
{RT @WestlifeFansite: hear @nickybyrneoffic on the radio one minute ago!! it was funny :D x}}
{\joinNameTweet
{WestlifeFansite}
{hear @nickybyrneoffic on the radio one minute ago!! it was funny :D x}}
\tweetRowFull{Non-tagged}
{0.579}
{\joinNameTweet
{esterrick}
{RIP Mr Brubeck. Take five. "@annesaurus: Dave Brubeck, jazz icon, dead at 91. http://t.co/ae9UIRmP"}}
{\joinNameTweet
{Supperphilly}
{RT @annesaurus: Dave Brubeck, jazz icon, dead at 91. http://t.co/sOrBOFBR}}
\tweetRowFull{Non-tagged}
{0.443}
{\joinNameTweet
{Zac\_Hartlage14}
{@BadJerry20 OKC traded James Harden}}
{\joinNameTweet
{24\_Jag}
{Why WOULD OKC TRADE JAMES HARDEN????}}
\tweetRowFull{Non-tagged}
{0.359}
{\joinNameTweet
{Serrae}
{(that should have had a link to the Tina and Amy host Golden Globes article. But I'm too lazy to fix it now)}}
{\joinNameTweet
{MichaelAusiello}
{Genius Move: Tina Fey and Amy Poehler to Host 2012 Golden Globe Awards! http://t.co/zdc2hS8F}}
\tweetRowFull{Non-tagged}
{0.275}
{\joinNameTweet
{nicoleoraha}
{@Niallofficial are you excited to come to Australia and meet all your amazing fans like me? ;) xx \#asknialler 11}}
{\joinNameTweet
{ahoynialler}
{@NiallOfficial EXCITED TO COME BACK TO AUSTRALIA, cause we miss you lots xox \#asknialler}}
\tweetRowFull{Non-tagged}
{0.242}
{\joinNameTweet
{Serrae}
{All of @fatherdowling's \#captainhottie pirate puns for \#ouat are perfect. It's the reason we are twitter friends.}}
{\joinNameTweet
{fatherdowling}
{I apologize in advance for inappropriate pirate puns. \#sorryImnotsorry \#OUAT}}
\tweetRowFull{Non-tagged}
{0.139}
{\joinNameTweet
{ESTL63}
{Forever my lady lol}}
{\joinNameTweet
{DaMontesMom\_415}
{@VictoriaLMathis just go get it!! Lol (the devil) aint I? Lol but I would lol}}
