\tweetRowFull{Retweet}
{1.0}
{\joinNameTweet
{brandonlondon}
{RT @neiltyson: A H R B Q D W E F L M N S X G I J K O P C T V Y U Z -- Gotta love what the alphabet looks like in alphabetical order.}}
{\joinNameTweet
{neiltyson}
{A H R B Q D W E F L M N S X G I J K O P C T V Y U Z -- Gotta love what the alphabet looks like in alphabetical order.}}

\tweetRowFull{Retweet}
{0.834}
{\joinNameTweet
{michael\_palko}
{RT @8\_Semesters: A girlfriend would be great, but I'm already in a pretty committed relationship with alcoholism and bad decisions.}}
{\joinNameTweet
{8\_Semesters}
{A girlfriend would be great, but I'm already in a pretty committed relationship with alcoholism and bad decisions.}}

\tweetRowFull{Retweet}
{0.768}
{\joinNameTweet
{mike\_sprague}
{RT @mshowalter: All the weird horny stuff between Glenn and Maggie on Walking Dead makes me very uncomfortable.}}
{\joinNameTweet
{mshowalter}
{All the weird horny stuff between Glenn and Maggie on Walking Dead makes me very uncomfortable.}}

\tweetRowFull{Retweet}
{0.602}
{\joinNameTweet
{\_\_ShesBrownSKIN}
{RT @\_CarGotThat: Brandywine Came Out With Win, \#TeamBwine}}
{\joinNameTweet
{\_CarGotThat}
{Brandywine Came Out With Win, \#TeamBwine}}

\tweetRowFull{Retweet}
{0.522}
{\joinNameTweet
{Becchappell}
{RT @oliviaaajayne\_: I just love Toy Story, all of them}}
{\joinNameTweet
{oliviaaajayne\_}
{I just love Toy Story, all of them}}

\tweetRowFull{Retweet}
{0.408}
{\joinNameTweet
{\_\_tiki}
{RT @Greektown1921: Welp now you know}}
{\joinNameTweet
{Greektown1921}
{Welp now you know}}

\tweetRowFull{Retweet}
{0.303}
{\joinNameTweet
{terrigolas}
{RT @jam\_bu88: Facebook is down? Oh no, how are cancer and child abuse going to stop without all those likes? :(}}
{\joinNameTweet
{dsilverman}
{RT @CalebGarling: Stop acting like we have ‘rights' on Facebook http://t.co/geE9NjHH}}

\tweetRowFull{Retweet}
{0.248}
{\joinNameTweet
{Becchappell}
{RT @j4kebro: going to be slightly awkward when Jahmene scans the xfactor winner's single in Asda}}
{\joinNameTweet
{bombaytricycle}
{RT @justaholyfooool: Jahmene is gonna be scanning James Arthers CD at ASDA now.. awks}}

\tweetRowFull{Retweet}
{0.132}
{\joinNameTweet
{HollywoodLadyj}
{RT @RealSkipBayliss: RG3 should give Michael Vick a class in scrambling.}}
{\joinNameTweet
{ESPN\_FirstTake}
{RG3 running at 4G!}}

\tweetRowFull{Retweet}
{0.070}
{\joinNameTweet
{davidAmejia}
{RT @Snoopy: It's Monday, Snoopy! http://t.co/asOF9yPA}}
{\joinNameTweet
{AshKetchum151}
{Mondays are like Zubats. Nobody likes Zubats.}}
