\tweetRowFull{Reply}
{0.768}
{\joinNameTweet
{esterrick}
{RT @StationBistro1: On deck - Next week's soup is White Bean and Smoked Turkey Chili!}}
{\joinNameTweet
{StationBistro1}
{On deck - Next week's soup is White Bean and Smoked Turkey Chili!}}

\tweetRowFull{Reply}
{0.693}
{\joinNameTweet
{Serrae}
{@MollytheGhost @PhantomRat @hollye83 @hockeybychoice @onlymystory @sjopierce @phouse1964 Hate them.}}
{\joinNameTweet
{hollye83}
{@hockeybychoice @onlymystory @PhantomRat @sjopierce @phouse1964 @MollytheGhost @Serrae Hateful. Just hateful.}}

\tweetRowFull{Reply}
{0.573}
{\joinNameTweet
{HectorBesmonte}
{@EmmittWard @jccassiel @hottiemarkie33 @mark\_purdie @Rhino108 @JasonReedyOH420 yeah! thanks emmit! muah! love, Hugs! for you!}}
{\joinNameTweet
{EmmittWard}
{@HectorBesmonte @jccassiel @hottiemarkie33 @mark\_purdie @Rhino108 @JasonReedyOH420 happy birthday hector sending you love and hugs buddy.}}

\tweetRowFull{Reply}
{0.477}
{\joinNameTweet
{VinnyG5}
{@shanmilanowski I wasn't really that drunk that day...I wouldn't get hammered and let you drive with me...but that's a secret so shhhhh}}
{\joinNameTweet
{shanmilanowski}
{RT @VinnyG5: @shanmilanowski lets do that thing were we get drunk and drive around the city while I'm playing my guitar ......again.}}

\tweetRowFull{Reply}
{0.386}
{\joinNameTweet
{RazWorth}
{@SophieRaby yeah! Buzzin}}
{\joinNameTweet
{SophieRaby}
{@RazWorth do you? :(}}

\tweetRowFull{Reply}
{0.283}
{\joinNameTweet
{SarahMcCallumXX}
{@SarahMcCallumXX @mton1996 forgot the x hahaa}}
{\joinNameTweet
{mton1996}
{@SarahMcCallumXX aw hen, I feel for you x}}

\tweetRowFull{Reply}
{0.245}
{\joinNameTweet
{missRaichl}
{@michel\_andness good morning!}}
{\joinNameTweet
{Michel\_andNess}
{Good morning everyone.}}

\tweetRowFull{Reply}
{0.168}
{\joinNameTweet
{Mahalia\_Enares}
{@kiafranklins\_ HAPPY BIRTHDAY!:) xx}}
{\joinNameTweet
{istoleursmartie}
{@Mahalia\_Enares i can be!!}}

\tweetRowFull{Reply}
{0.133}
{\joinNameTweet
{MeganDoesNOLA}
{@KurlyKonfektion Niiiiice...}}
{\joinNameTweet
{KurlyKonfektion}
{@MeganDoesNOLA lmao! I'm gonna put a slice of bacon with/in my drink and see what happens lol}}

\tweetRowFull{Reply}
{0.068}
{\joinNameTweet
{essfardella}
{@Ali\_Diesel\_ There it is.}}
{\joinNameTweet
{Ali\_Diesel\_}
{RT @shkeeber: I am not a slut.    I'm an erection enthusiast.}}